What We Eval in the Shadows

### 2021-04-04 paper/main.tex
Working on provenance

\mypara{Source.}
There are various ways to obtain expressions:
\begin{itemize}
  \item \c{substitute} synthesizes ASTs from expressions by replacing
    symbols with their bindings in the specified environment.
  \item \c{expression}  creates a vector of expression
    objects from text.
  \item \c{parse}, \c{str2expression} and \c{str2lang} turn strings into
    expressions.
\end{itemize}

@@

\section{\eval patterns and anti-patterns}

\subsection{Evaluating variables in a specific environment}

@@

\subsection{Meta-programming}

@@

>>>>

\mypara{Source.} % rename to provenance

% Substitute/match.call
% parse/expression
% bytecode?

There are various ways to obtain expressions:
\begin{itemize}
  \item \c{substitute} synthesizes ASTs from expressions by replacing
    symbols with their bindings in the specified environment.
  \item \c{expression}  creates a vector of expression
    objects from text.
  \item \c{parse}, \c{str2expression} and \c{str2lang} turn strings into
    expressions.
\end{itemize}

@@

\section{Usage of \eval}

We present here the main uses of \eval we have witnessed in R. Sometimes, they are design patterns, sometimes, \eval could be replaced by more specific functions. For each use of \eval, we discuss whether it is necessary to use.

\subsection{Variable lookup}

\eval is used to look-up the value of a variable in a given environment, different from the current scope so the \c{envir} argument of \eval is explicitly specified.

% TODO: numbers on the prevalence of the pattern

\eval is not necessary in that case and can be replaced by \c{get}, as follows:

\begin{lstlisting}
 eval(quote(x), envir = env)
\end{lstlisting}
$\Downarrow$
\begin{lstlisting}
get("x", envir = env)
\end{lstlisting}

% This is actually linked to NSE, as the symbol given to \eval usually comes
% from match.call or susbtitute

\subsection{Non-Standard Evaluation} % Or metaprogramming

\subsection{\c{substitute}}

@@

@@

% Derivation of symbolic expressions
